---
title: "R_alike project 03"
description: "Coefficient plots"
date: "`r Sys.Date()`"
author:
  - name: Radoslaw Panczak 
    url: https://github.com/RPanczak
    affiliation: ISPM
    affiliation_url: https://www.ispm.unibe.ch/
    orcid_id: 0000-0001-5141-683X
# bibliography: biblio.bib
output:
  distill::distill_article:
    highlight: pygments
    toc: true
    toc_depth: 1
    number_sections: true
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../docs") })
---
  
```{r rsetup, include=FALSE}
options(scipen=999)
set.seed(12345)

library(pacman)
```

```{r conflicts, include = FALSE}
# tidyverse::tidyverse_conflicts()

conflicted::conflict_scout()
```

```{r knit-setup, include = FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

knitr::opts_chunk$set(cache = FALSE,
                      prompt = FALSE,
                      tidy = FALSE,
                      comment = NA,
                      message = FALSE,
                      warning = FALSE,
                      echo = TRUE,
                      dpi=300)

knitr::opts_knit$set(width = 75)
```

<!-- ------------------------------------------ -->

# Setup

## Data 

**Outbreak investigation** from `epiDisplay` package - containing information from an outbreak investigation concerning food poisoning on a sportsday in Thailand 1990.

> Thaikruea, L., Pataraarechachai, J., Savanpunyalert, P., Naluponjiragul, U. 1995 An unusual outbreak of food poisoning. *Southeast Asian J Trop Med Public Health* **26(1)**:78-85.

Data described:
https://cran.r-project.org/web/packages/epiDisplay/epiDisplay.pdf

Data preparation described:
https://assets.publishing.service.gov.uk/media/57a08ba9ed915d622c000e0b/epicalc.pdf

```{r}
p_load(epiDisplay)
data(Outbreak)
data <- Outbreak

data$case <- (data$nausea==1)|(data$vomiting==1)|(data$abdpain==1)|(data$diarrhea==1)

data <- data[c("case", "sex", "age", "eclair",
               "beefcurry", "saltegg", "water")]

data$age <- data$age/10
data$sex <- as.factor(data$sex)
data$age[data$age == 99] <- NA

data$beefcurry[data$beefcurry == 9] <- NA
data$saltegg[data$saltegg == 9] <- NA
data$water[data$water == 9] <- NA

data$eclair[data$eclair == 90] <- NA

data$eclair <- cut(data$eclair, 
                   breaks = c(0, 0.4, 1, 2, 79),
                   include.lowest = TRUE, 
                   labels=c("0","1","2",">2")) 

data$beefcurry <- as.factor(data$beefcurry)
data$saltegg <- as.factor(data$saltegg)
data$water <- as.factor(data$water)

mosaicplot(~ eclair + case, data = data, color = TRUE)
mosaicplot(~ beefcurry + case, data = data, color = TRUE)
mosaicplot(~ saltegg + case, data = data, color = TRUE)
mosaicplot(~ water + case, data = data, color = TRUE)
```

## Dummy model 

```{r}
model <- glm(case ~ age + sex + eclair, 
             data = data, 
             family = binomial)
```

## Summary

```{r}
summary(model)
```

ORs & CI to plot:

```{r message=FALSE}
cbind(exp(coef(model)), exp(confint(model)))
```

## Diagnostics 

```{r}
par(mfrow = c(2, 2))
plot(model)
```

```{r include=FALSE}
dev.off()
```

<!-- ------------------------------------------ -->

# `jtools` package 

```{r include=FALSE}
p_load(jtools, ggplot2)
```

## Alternative summary 

<aside>
CI are not `exp()`?
</aside>

```{r}
summ(model, exp = TRUE, confint = TRUE)
```

## Plot

```{r}
plot_coefs(model, exp = TRUE) + scale_x_log10()
```

```{r include=FALSE}
p_unload(jtools, ggplot2)
```

<!-- ------------------------------------------ -->

# `sjPlot` package 

```{r include=FALSE}
p_load(sjPlot, ggplot2)
```

## Plot

<aside>
Seem to get almost everything out of the box?
</aside>

```{r}
plot_model(model) + geom_hline(yintercept = 1, color = "grey40")
```

```{r include=FALSE}
p_unload(sjPlot, ggplot2)
```

<!-- ------------------------------------------ -->

# `see` & `parameters` packages

```{r include=FALSE}
p_load(see, parameters, performance)
```

## Alternative summary 

```{r}
model_parameters(model, exponentiate = TRUE)
```

## Plot

<aside>
`exponentiate = TRUE` needed in both calls!
</aside>

```{r}
result <- model_parameters(model, exponentiate = TRUE)

plot(result, exponentiate = TRUE, size_text = 4)
```

## Diagnostics 

```{r}
model_performance(model)

check_model(model)
```

```{r include=FALSE}
p_unload(see, parameters, performance)
```

<!-- ------------------------------------------ -->

# `forestmodel` package 

```{r include=FALSE}
p_load(forestmodel)
```

## Plot

<aside>
Nicely adds **N** & ref. categories!
</aside>

```{r}
forest_model(model) 
```

```{r include=FALSE}
p_unload(forestmodel)
```

<!-- ------------------------------------------ -->

# `modelsummary` package 

```{r include=FALSE}
p_load(modelsummary)
```

## Plot

<aside>
But how to `exp()`? `exponentiate = TRUE` should work according to help but doesn't :/
</aside>

```{r}
modelplot(model, coef_omit = 'Interc') + 
  geom_vline(xintercept = 0, color = "grey40")
```

```{r include=FALSE}
p_unload(modelsummary)
```


<!-- ------------------------------------------ -->

# `arm` package 

```{r include=FALSE}
p_load(arm)
```

## Plot

<aside>
But how to `exp()`? :/
</aside>

```{r}
coefplot(model)
```

```{r include=FALSE}
p_unload(arm)
```

<!-- ------------------------------------------ -->

# `GGally` package 

```{r include=FALSE}
p_load(GGally)
```

## Plot

```{r}
ggcoef(model, exponentiate = TRUE, exclude_intercept = TRUE)
```

```{r include=FALSE}
p_unload(GGally)
```

<!-- ------------------------------------------ -->

# `ggstatsplot` package 

```{r include=FALSE}
p_load(ggstatsplot)
```

## Plot

```{r}
ggcoefstats(
  x = model,
  exponentiate = TRUE
)
```

```{r include=FALSE}
p_unload(ggstatsplot)
```

<!-- ------------------------------------------ -->

# `dotwhisker` package 

```{r include=FALSE}
p_load(dotwhisker)
```

## Plot

```{r}
dwplot(model, exponentiate = TRUE) + 
  scale_x_log10() + 
  geom_vline(xintercept = 1, color = "grey40")
```

```{r include=FALSE}
p_unload(dotwhisker)
```

<!-- ------------------------------------------ -->

# `visibly` package 

```{r include=FALSE}
p_load(visibly)
```

## Plot

```{r}
plot_coefficients(model, trans = exp) + 
  scale_y_log10() + 
  geom_hline(yintercept = 1, color = "grey40")
```

```{r include=FALSE}
p_unload(visibly)
```

<!-- ------------------------------------------ -->

# `visreg ` package 

```{r include=FALSE}
p_load(visreg)
```

## Plot

<aside>
Not really coefficients... Can be also done as ggplot with `gg = TRUE`
</aside>

```{r}
par(mfrow = c(1, 3))
visreg(model)# , gg = TRUE)
```

```{r include=FALSE}
p_unload(visreg)
dev.off()
```
